---
title: "LLM Experiment"
author: "Maria Cuellar"
date: today
resource-path:
  - ..
format:
  html:
    toc: true
    toc-location: body
    toc-depth: 2
    number-sections: true
    code-fold: true
    code-summary: "Show code"
execute:
  echo: true
  warning: false
  message: false
---

This report summarizes a controlled multi-model audit of paired SBS/AHT or forensic vignettes. The OpenAI workflow uses the Responses API with Structured Outputs so the output schema is enforced in the request rather than only described in the prompt. The analysis is structured around within-pair comparisons rather than treating repeated model calls as independent subjects.

```{r setup}
library(dplyr)
library(readr)
library(knitr)
library(ggplot2)
library(tidyr)
library(stringr)

summary_path <- "../results/paired_summary.csv"
parsed_path <- "../results/parsed_outputs.csv"
plot_path <- "../figures/abuse_probability_diff_by_model.png"

summary_exists <- file.exists(summary_path)
parsed_exists <- file.exists(parsed_path)
plot_exists <- file.exists(plot_path)

if (summary_exists) {
  paired_summary <- read_csv(summary_path, show_col_types = FALSE)
}

if (parsed_exists) {
  parsed_outputs <- read_csv(parsed_path, show_col_types = FALSE)
}
```

# Overview

The project uses:

- a fixed system prompt
- a small set of fixed user prompt templates
- `gpt-5.5` via the OpenAI Responses API
- Structured Outputs with a strict JSON schema
- stateless API calls
- CSV-based storage for raw and parsed outputs
- paired comparisons within vignette

# Workflow

Render the Quarto documents from the repository root in this order:

```bash
quarto render analysis/run_experiment.qmd
quarto render analysis/parse_results.qmd
quarto render analysis/analyze_results.qmd
```

Then re-render this Quarto document.

# Current Inputs

```{r}
knitr::kable(read_csv("../vignettes.csv", show_col_types = FALSE))
```

# Parsed Output Snapshot

```{r}
if (parsed_exists) {
  parsed_outputs %>%
    select(provider, model, prompt_template, pair_id, condition_label,
           classification, abuse_probability, report_to_cps, confidence,
           parse_status, error_message) %>%
    head(12) %>%
    knitr::kable()
} else {
  cat("`results/parsed_outputs.csv` does not exist yet. Render `parse_results.qmd` first.")
}
```

# Paired Summary Table

```{r}
if (summary_exists) {
  paired_summary %>%
    arrange(provider, model, prompt_template, target_attribute) %>%
    knitr::kable(digits = 2)
} else {
  cat("`results/paired_summary.csv` does not exist yet. Render `analyze_results.qmd` first.")
}
```

# Paired Difference Plot

```{r, fig.width=10, fig.height=6}
if (plot_exists) {
  knitr::include_graphics(plot_path)
} else {
  cat("`figures/abuse_probability_diff_by_model.png` does not exist yet. Render `analyze_results.qmd` first.")
}
```

# Notes

This report intentionally centers paired differences. The key estimands are changes within the same vignette pair when only one socially salient but normatively irrelevant attribute is altered.

Repeated calls can still be useful for sensitivity checks, but they should not be interpreted as independent survey respondents.
