---
title: "Parse Results"
format:
  html:
    toc: true
execute:
  echo: true
  warning: false
  message: false
---

This document parses raw LLM outputs into structured columns and saves the result to `results/parsed_outputs.csv`.

```{r}
suppressPackageStartupMessages({
  library(dplyr)
  library(jsonlite)
  library(readr)
  library(stringr)
  library(tibble)
})
```

## Configuration

```{r}
raw_results_path <- file.path("..", "results", "raw_outputs.csv")
parsed_results_path <- file.path("..", "results", "parsed_outputs.csv")

dir.create(dirname(parsed_results_path), recursive = TRUE, showWarnings = FALSE)
```

## Helpers

```{r}
strip_json_fences <- function(text) {
  if (is.na(text) || !nzchar(text)) {
    return(NA_character_)
  }

  cleaned <- text %>%
    str_replace("^```json\\s*", "") %>%
    str_replace("^```\\s*", "") %>%
    str_replace("\\s*```$", "") %>%
    str_trim()

  cleaned
}

extract_json_object <- function(text) {
  if (is.na(text) || !nzchar(text)) {
    return(NA_character_)
  }

  cleaned <- strip_json_fences(text)
  match <- str_match(cleaned, "(\\{[\\s\\S]*\\})")
  json_candidate <- match[, 2]

  if (is.na(json_candidate) || !nzchar(json_candidate)) {
    return(cleaned)
  }

  json_candidate
}

to_bool <- function(x) {
  if (is.logical(x) && length(x) == 1) {
    return(x)
  }

  if (is.character(x) && length(x) == 1) {
    x_lower <- tolower(trimws(x))
    if (x_lower %in% c("true", "t", "yes", "1")) return(TRUE)
    if (x_lower %in% c("false", "f", "no", "0")) return(FALSE)
  }

  NA
}

to_bounded_number <- function(x, min_value = 0, max_value = 100) {
  val <- suppressWarnings(as.numeric(x))

  if (length(val) == 0 || is.na(val)) {
    return(NA_real_)
  }

  if (val < min_value || val > max_value) {
    return(NA_real_)
  }

  val
}

`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0 || is.na(x)) y else x
}

safe_parse_output <- function(raw_text) {
  cleaned_json <- extract_json_object(raw_text)

  if (is.na(cleaned_json) || !nzchar(cleaned_json)) {
    return(tibble(
      parse_status = "no_text",
      parse_error = "No response text available.",
      cleaned_json = NA_character_,
      classification = NA_character_,
      abuse_probability = NA_real_,
      report_to_cps = NA,
      confidence = NA_real_,
      reasoning_summary = NA_character_
    ))
  }

  parsed <- tryCatch(
    fromJSON(cleaned_json),
    error = function(e) e
  )

  if (inherits(parsed, "error")) {
    return(tibble(
      parse_status = "parse_failed",
      parse_error = conditionMessage(parsed),
      cleaned_json = cleaned_json,
      classification = NA_character_,
      abuse_probability = NA_real_,
      report_to_cps = NA,
      confidence = NA_real_,
      reasoning_summary = NA_character_
    ))
  }

  classification <- parsed$classification %||% NA_character_
  allowed_classes <- c("abuse", "indeterminate", "not_abuse")

  if (!is.character(classification) || length(classification) != 1 || !(classification %in% allowed_classes)) {
    classification <- NA_character_
  }

  tibble(
    parse_status = "parsed",
    parse_error = NA_character_,
    cleaned_json = cleaned_json,
    classification = classification,
    abuse_probability = to_bounded_number(parsed$abuse_probability),
    report_to_cps = to_bool(parsed$report_to_cps),
    confidence = to_bounded_number(parsed$confidence),
    reasoning_summary = as.character(parsed$reasoning_summary %||% NA_character_)
  )
}
```

## Parse Outputs

```{r}
raw_results <- read_csv(raw_results_path, show_col_types = FALSE)

parsed_results <- raw_results %>%
  rowwise() %>%
  do(bind_cols(as_tibble(.), safe_parse_output(.$raw_response))) %>%
  ungroup()

write_csv(parsed_results, parsed_results_path)

cat("Parsed results saved to:", parsed_results_path, "\n")
cat("Rows parsed:", nrow(parsed_results), "\n")
```
